R for Clinical Study Reports and Submission

### 2022-12-18 slides/r4csr-gwu.Rmd
update package name style (#91)
- avoid inline style for packge name

- [`r2rtf`](https://merck.github.io/r2rtf/): create production-ready tables and figures in RTF format.
- [`pkglite`](https://merck.github.io/pkglite/): represent and exchange R package source code as text files.
- `cleanslate` (under internal validation): create portable R environments.

@@

`r2rtf` is designed to:

@@

`r2rtf` is designed to be pipe-friendly (`%>%`)

@@

- As a statistician, I use `tidyverse`, `r2rtf`,
and internal tools to define the mock-up table, listing and figure (TLFs) for statistical analysis of a clinical trial.
  - More than 100 TLFs for efficacy and safety of a drug or vaccine.

- As a programmer, I use `tidyverse`, `r2rtf`, and internal tools to develop and/or validate analysis results based on mock-up TLFs.

>>>>

- [r2rtf](https://merck.github.io/r2rtf/): create production-ready tables and figures in RTF format.
- [`pkglite`](https://merck.github.io/pkglite/): represent and exchange R package source code as text files.
- `cleanslate` (under internal validation): create portable R environments.

@@

r2rtf is designed to:

@@

r2rtf is designed to be pipe-friendly (`%>%`)

@@

- As a statistician, I use tidyverse, r2rtf,
and internal tools to define the mock-up table, listing and figure (TLFs) for statistical analysis of a clinical trial.
  - More than 100 TLFs for efficacy and safety of a drug or vaccine.

- As a programmer, I use tidyverse, r2rtf, and internal tools to develop and/or validate analysis results based on mock-up TLFs.

### 2022-12-18 tlf-efficacy-ancova.Rmd
update package name style (#91)
- avoid inline style for packge name

The `emmeans` R package is used to obtain
within and between group least square (LS) mean

@@

Then `r2rtf` is used to prepare the table format for `t1`.
We also highlight how to handle special characters in this example.

Special characters `^` and `_` are used to define superscript and subscript of text. And `{}` is to define the part that will be impacted.
For example, `{^a}` provides a superscript `a` for footnote notation.
`r2rtf` also supports most LaTeX characters.
Examples can be found on the
[`r2rtf` get started page](https://merck.github.io/r2rtf/articles/r2rtf.html#special-character).
The `text_convert` argument in `r2rtf_*()` functions controls whether to convert special characters.

@@

We also use `r2rtf` to prepare the table format for `t2`

@@

Finally, we combine the two parts to get the final table using `r2rtf`.
This is achieved by providing a list of `t1_rtf` and `t2_rtf` as input for
`rtf_encode`.

>>>>

The emmeans R package is used to obtain
within and between group least square (LS) mean

@@

Then r2rtf is used to prepare the table format for `t1`.
We also highlight how to handle special characters in this example.

Special characters `^` and `_` are used to define superscript and subscript of text. And `{}` is to define the part that will be impacted.
For example, `{^a}` provides a superscript `a` for footnote notation.
r2rtf also supports most LaTeX characters.
Examples can be found on the
[r2rtf get started page](https://merck.github.io/r2rtf/articles/r2rtf.html#special-character).
The `text_convert` argument in `r2rtf_*()` functions controls whether to convert special characters.

@@

We also use r2rtf to prepare the table format for `t2`

@@

Finally, we combine the two parts to get the final table using r2rtf.
This is achieved by providing a list of `t1_rtf` and `t2_rtf` as input for
`rtf_encode`.

### 2022-12-18 tlf-efficacy-km.Rmd
update package name style (#91)
- avoid inline style for packge name

The `survival` package is used to obtain the K-M estimate.

@@

Now, we can use the `r2rtf` package to create a formatted RTF figure.
More details can be found on the [r2rtf website](https://merck.github.io/r2rtf/articles/example-figure.html).

@@

- Step 1: Read the data `adtte` into R.
- Step 2: Define the analysis-ready dataset. In this example, we define the analysis dataset for the TTDE endpoint `adtte_ttde`.
- Step 3: Save figures into `png` files based on required analysis specification.
- Step 4: Create RTF output using the `r2rtf` package.

>>>>

The survival package is used to obtain the K-M estimate.

@@

Now, we can use the r2rtf package to create a formatted RTF figure.
More details can be found on the [r2rtf website](https://merck.github.io/r2rtf/articles/example-figure.html).

@@

- Step 1: Read the data `adtte` into R.
- Step 2: Define the analysis-ready dataset. In this example, we define the analysis dataset for the TTDE endpoint `adtte_ttde`.
- Step 3: Save figures into `png` files based on required analysis specification.
- Step 4: Create RTF output using the r2rtf package.
